A fast primal-dual algorithm for computing best response strategies in two-person sequential games

### 2014-07-27 paper.tex
paper improved

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $A^T$: \quad transpose of the matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: vertical stacking of the matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of the vector $v$;
\item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
\item $\mathbb{R}_+$: \quad the nonnegative part of the real-line $\mathbb{R}$;
\item $(x)_+$: \quad the component-wise maximum of the vector $x$ and 0;
\item $i_C$: \quad the indicator function of the convex set $C$;
\item $\Pi_C$: \quad the euclidean projector onto the convex set $C$;
\item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
\item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
\item \textit{l.s.c}: \quad acronyme for ``lower semi-continuous'';
\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\end{itemize}

>>>>

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathbb{R}^{m, n}$ \quad the space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under the matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\item $A^T$: \quad the transpose of the matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad the vertical stacking of the matrices $A$ and $B$;
\item $v_j$: \quad the $j$th component of the vector $v$;
\item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
\item $\mathbb{R}_+$: \quad the nonnegative part of the real-line $\mathbb{R}$;
\item $(x)_+$: \quad the component-wise maximum of the vector $x$ and 0;
\item $i_C$: \quad the indicator function of the convex set $C$;
\item $\Pi_C$: \quad the euclidean projector onto the convex set $C$;
\item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
\item \textit{l.s.c}: \quad acronym for \textit{lower semi-continuous};
\item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
\end{itemize}
